Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
edited shou-wu's easy comments

\begin{defn}
\label{defn:h0-stacky}
Recall the standard notation 
$$\sco(D) := \{f \in \Bk(X)^\times : \di f + D \geq 0 \}.$$
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define
\begin{align*}
	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
\end{align*}
If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
graded component of $R$.

@@

\begin{example}
\label{eg:base-1-0}
Let $(\sx',0, \halfcan')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$.
Counting dimensions, we see $h^0(\sx, k\halfcan')=1$ for all $k \in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong \Bk[x]$ with $x$ a generator in degree 1.
\end{example}

\begin{example}
\label{eg:adding-point}
Let $\sx$ be a stacky curve with coarse space $X$ and signature $(0
; 3; 3)$. Let $P_1$ denote the lone stacky point which has stabilizer
order $3$ and suppose $\infty$ is a fixed closed point of $X$ that is
not equal to $P_1$.

We will deduce the structure of the log spin canonical ring $R_L$
from the structure of the spin canonical ring $R_{L_X} := R(X, 3
\cdot \infty, L_X)$. This technique will later be generalized in Lemma ~\ref{lem:sat-1}.

>>>>

\begin{defn}
\label{defn:h0-stacky}
Recall the standard notation for the line bundle $\sco(D)$ on an integral normal scheme $X$ associated to a divisor $D \in \di X$:
$$\Gamma(U, \sco(D)) := \{f \in \Bk(X)^\times : \di|_U f + D|_U \geq 0 \}.$$
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define
\begin{align*}
	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
\end{align*}
If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
graded component of $R$.

@@

\begin{example}
\label{eg:base-1-0}
Let $(\sx',0, \halfcan')$ be a log spin curve of genus $g = 1,$ with $\halfcan' = 0$.
Counting dimensions, we see $h^0(\sx, k\halfcan')=1$ for all $k \in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong \Bk[x]$ with $x$ a generator in degree 1.
\end{example}

\begin{example}
\label{eg:adding-point}
Let $(\sx,3 \cdot \infty, L)$ be a stacky curve with coarse space $X$ and signature 
$(0; 3; 3)$. Let $P_1$ denote the lone stacky point which has stabilizer
order $3$ and suppose $\infty$ is a fixed closed point of $X$ that is
not equal to $P_1$.

Recall the notation $L_X = \lfloor L \rfloor \in \di X$. We will deduce the structure of the log spin canonical ring $R_L$
from the structure of the spin canonical ring $R_{L_X} := R(X, 3
\cdot \infty, L_X)$. This technique will later be generalized in Lemma ~\ref{lem:sat-1}.
